Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-07-21 ms.tex
corrected spelling of bochinski.

In order to understand the long term behavior of the \sha\ system, we summarize the available published photometry in Table \ref{tab:prevObs}
The Kepler mission provided the longest time baseline with near continuous photometry for about 4 years in long cadence ($\sim$30 min) mode.
Following the failure of the reaction wheel, there were a few follow-up ground based observations.
\citet{bochinsky2015evolving} obtained multi-color simultaneous photometry ($u'$, $g'$ and $z'$) to characterize the dust in the system.
The ratio of the $g'$ to $z'$ transit depths indeed deviated from unity, which could be fit with an interstellar dust extinction law.
Overall, \citet{bochinisky2015evolving} observed 5 separate nights spanning the expected transit durations and detect 1 transit $\sim$1\% in $g'$ band, 1 transit $\sim$0.1\% in $g'$ band and 3 upper limits of < 0.03\% for the other nights.

>>>>

In order to understand the long term behavior of the \sha\ system, we summarize the available published photometry in Table \ref{tab:prevObs}
The Kepler mission provided the longest time baseline with near continuous photometry for about 4 years in long cadence ($\sim$30 min) mode.
Following the failure of the reaction wheel, there were a few follow-up ground based observations.
\citet{bochinski2015evolving} obtained multi-color simultaneous photometry ($u'$, $g'$ and $z'$) to characterize the dust in the system.
The ratio of the $g'$ to $z'$ transit depths indeed deviated from unity, which could be fit with an interstellar dust extinction law.
Overall, \citet{bochinski2015evolving} observed 5 separate nights spanning the expected transit durations and detect 1 transit $\sim$1\% in $g'$ band, 1 transit $\sim$0.1\% in $g'$ band and 3 upper limits of < 0.03\% for the other nights.
